Type Ia Supernova Explosions from Hybrid Carbon-Oxygen-Neon White Dwarf Progenitors

### 2019-03-21 paper/ms.tex
Updated lots of text, added some questions, marked text for removal.

The methodology of our study follows the approach of \citet{willcoxetal2016}.
We performed a suite of two-dimensional simulations of supernova explosions
from hybrid progenitors and compared the results to a suite of simulations
of explosions from traditional C/O progenitor models performed with the
same simulation code and from similar initial conditions. The simulations assumed
the deflagration to detonation transition explosion paradigm, and the
transition densities were the same in both suites. We briefly our methodology
here, and refer to the reader to previous work for additional details.
In particular, we use the same simulation instrument, a modified version
of the Flash Code, as \citet{willcoxetal2016} and we refer the reader there
for a description of modifications for C-O-Ne burning and verification tests
of the burning module.

@@

The simulations of supernova explosions presented here were performed
with a customized version of the \FLASH code, originally developed
at the University of Chicago.
Flash is a parallel, adaptive mesh, multi-physics simulation code
developed first for nuclear astrophysics applications and subsequently
for high-energy-density applications~\cite{Fryxetal00,calder.curtis.ea:high-performance,
calder.fryxell.ea:on,flash_pragmatic,flash_evolution}.
Flash has been applied to a variety of astrophysical problems by a host
of researchers, and the version we apply differs from other versions
principally in the modules describing thermonuclear burning via a
flame capturing model.

@@

For the deflagration phase, the flame capturing scheme propagates an
artificially broadened flame with an advection-diffusion-reaction (ADR)
scheme~\cite{Khok95,VladWeirRyzh06} via evolution of
a reaction progress variable to describe the consumption of C
and additional variables to describe the evolution of intermediate-mass
elements into the statistical quasi-equilibrium of the
Si-group~\cite{ifk1981,khok1981,khok1983} and then into iron-group elements
(IGEs) in full nuclear statistical equilibrium (NSE).

The reaction progress variable is $\phi$ and it varies from $\phi=0$ for
unburned fuel and $\phi=1$ for burned ash. $\phi$ is evolved
via an advection-diffusion-reaction equation,
\begin{equation}
  \label{eq:ard}
  \partial_t \pv + \vec{u}\cdot\nabla \pv = \kappa \nabla^2 \pv +
\frac{1}{\tau} R\left(\phi\right) ,
\end{equation}
where $\vec{u}$ is the velocity of the fluid, $\kappa$ is the
diffusion coefficient, $\tau$ is the reaction timescale, and $R(\phi)$ is
a non-dimensional function describing the reaction. The parameters
$\kappa$, $\tau$, and $R(\phi)$ are tuned to propagate the reaction
front at a prescribed speed.  Our model uses the ``sharpened KPP
 described by~\cite{VladWeirRyzh06},
with $R\propto(\phi-\epsilon)(1-\phi+\epsilon)$, where
$\epsilon \simeq 10^{-3}$.  This scheme has been shown to be
acoustically quiet, stable, and to give a unique flame speed
\cite{townsley.calder.ea:flame}. The input flame speeds come from
tabulated results obtained by direct numerical simulations of
thermonuclear burning~\cite{timmes92,Chamulak2007The-Laminar-Fla},
and
these are boosted to account for speed-up of burning due to unresolved
buoyancy and background turbulence~\cite{Khok95,
gamezo.khokhlov.ea:thermonuclear,townsley.calder.ea:flame,jacketal2014}.

The two-dimensional models in this study do not utilize a sub-grid-scale
model for the turbulence-flame
interaction~\citep[See][for examples]{Schmetal06a,Schmetal06b,jacketal2014},
The models only apply in three-dimensional
simulations because two-dimensional hydrodynamics cannot
correctly describe turbulence. The simulations we present
use the minimal enhancement based on the Rayleigh-Taylor
strength introduced by~\citet{townsley.calder.ea:flame}. The
assumption here is that the burning self-regulate on resolved
scales so that results are insensitive to the detailed treatment
of the interaction with turbulence, and previous experience
indicates this assumption is reasonable for comparisons
like the one presented in this work~\citet{townsley.calder.ea:flame,
willcoxetal2016}.

The ADR scheme describes the consumption of C and the subsequent stages
are described by separate progress variables and
separate relaxation times derived from full nuclear network calculations
\cite{Caldetal07,townetal2016}. In both the quasi-equilibrium and full equilibrium,
the creation of light elements by photodisintegration balances the creation of heavy
elements by fusion, maintaining the equilibrium. The relative balance depends on
thermodynamic conditions, e.g.\ density and temperature, and hydrodynamic motion
during the explosion changes the thermodynamic conditions and thus the
balance. Electron capture also influences the evolution by shifting the binding
energy of the material and thereby changing the temperature due to released energy,
by changing the Fermi energy and thus the pressure, and by emitting neutrinos that
escape and remove energy. Electron captures also neutronize the material, which
produces more neutron rich iron-group material at the expense of \Ni. Like the
input flame speed, the burning model includes tabulated rates for these effects
from detailed NSE calculations ~\cite{SeitTownetal09}. Accordingly, the burning
model is able to describe dynamic evolution of the ash in addition to the
stages of C-O-Ne burning.

The burning model also describes the detonation phase with progress variables.
In this case, the model evolves thermally-activated burning with the actual
temperature-dependent rate for C consumption, which allow a propagating shock to
trigger burning, i.e.\ to propagate a detonation front. The propagating detonation
is able to describe the same stages of C burning as the deflagration case, including
the relaxation into NSE~\cite[and references therein]{townetal2016}. Finally,
we again note that the burning model was adapted for the case of burning in
hybrid white dwarfs. Direct numerical simulations of burning that guided
the modifications, details of the modifications to the burning model, and
verification tests may be found in \citet{willcoxetal2016}.

@@

The hybrid white dwarf model that served as the initial conditions
for the simulations of supernova explosions presented in this work
was constructed with the one-dimensional stellar evolution code
MESA~\citep{mesa1,mesa2,mesa3,mesa3e}. The evolution of the model
included thermohalene mixing during the cooling phase and thus
had a lower C fraction than previous hybrid models~\citep{brooksetal2017}.
The hybrid model was constructed to have conditions as similar a possible
to a ``classic" C/O model and the two shared the same central temperature
and density.  Figure~\ref{fig:init_conds} shows the density and temperature
profiles of the two initial one-dimensional models.
\begin{figure}
\includegraphics[width=\columnwidth]{figures/initial_conds.png}
\caption{\label{fig:init_conds}
Temperature, density, and  composition profiles of the one-dimensional hybrid
progenitor WD. The central temperature and density were the same as
the traditional C/O progenitor model.
The peak temperature of the hybrid model is at the center of the star,
so both the hybrid and traditional models could share the same
	central ignition initial conditions.
}
\end{figure}
In both models, and unlike the hybrid models of~\citet{willcoxetal2016}, the central
temperature was the highest at the center of the star and accordingly the simulations
began with central ignitions.

@@

The initial progenitor models for the two-dimensional simulations were
created from the one-dimensional \MESA\ models by mapping the one-dimensional
models onto the two-dimensional domain while
preserving hydrostatic equilibrium.
As described above, the flame capturing scheme with progress
variables describing the evolution as the material burns. The \MESA\
models, however, relied on a detailed reaction network that included
many species. Accordingly, the process of creating the two-dimensional
models for \FLASH\ required aggregating some of the species abundances.
As with much of this study, we applied the
techniques of~\citet{willcoxetal2016}.

The process of mapping the \MESA\ models began by converting
the \MESA\ model to a uniform grid of $4$~km resolution. \MESA\
quantities in zones with spacing less than $4$~km
were mass-weighted averaged and a quadratic interpolation
was used to calculate quantities for the case of \MESA\ zones having
a spacing greater than $4$~km. At this point,
abundances of nuclides from the \MESA\ models were aggregated
into the abundances tracked by the flame capturing scheme in
\FLASH.
The most abundant isotopes in the model were \C{12}, \Ox{16},
and \Ne{20}, which are symmetric (the number of neutrons
equals the number of protons). Similarly to~\citet{willcoxetal2016},
other neutron-rich isotopes in the initial model were combined into
\Ne{22}, which serves as a proxy for metallicity. The aggregation
account for the $Y_e$ of the full set of nuclides, \Ne{20}
and \Ox{16} were constrained to be in the same ratio in both
sets of abundances. \figref{fig:init_conds} shows the initial
profile of the one-dimensional models.

The original \MESA\ model was in equilibrium, but to ensure
the uniformly-gridded model was in hydrostatic equilibrium we
constructed the appropriate pressure profile. This was done by
integrating for the pressure in each zone from the central point up,
accounting for the local acceleration of gravity, temperature,
composition, and the mass below and enclosed by the zone. As
with \citet{willcoxetal2016} we used
EOS routine from
\CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.\footnote{The
Helmholtz EOS table used in \CASTRO\ is in the public BoxLib
Microphysics repository at
  \url{https://github.com/BoxLib-Codes/Microphysics.git} (commit
  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).} As
 with the models in \citet{willcoxetal2016},this procedure produced
 a structure that was stable in \FLASH, with fluctuations in central
density less than $3\%$, for at least $5$ seconds with no energy
deposition.

\subsection{DDT Process and Suits of Explosions}

The simulations performed for this study consisted to a suite of
{\color{red} 35 CHECK THIS! 40?} two-dimensional simulations of
thermonuclear supernova
explosions from hybrid C-O-Ne progenitors in the DDT explosion paradigm. These
were compared to a suite of supernova simulations from traditional
C-O progenitors. In both suites, the simulation
begins with a progenitor model mapped to the two-dimensional
\FLASH\ grid. The burning is initiated with a ``match head,'' a region
in the white dwarf's center that is fully burned to nuclear statistical
equilibrium (NSE).
This initially burned region ignites a deflagration, a subsonic
flame, and because the match head was perturbed it is unstable to
the Rayleigh-Taylor instability with the result that buoyant plumes
rise. The star is partially consumed during this deflagration phase,
and the star responds by expanding.
When a plume reaches a specified density,
a detonation is initiated, and the simulation continues until
the expanding star reaches low densities at which point burning
effectively ends. The paragraphs in this section provide details
of the implementation of this method.

@@

The simulations were performed in two-dimensional $\mathrm{z-r}$
cylindrical coordinates, extending radially from 0 to
$65,536$~\km\ and along the axis of symmetry from $-65,536$~\km\ to
$65,536$~\km. The maximum refinement level of the adaptive mesh
corresponded to $4$~\km\ resolution, which previous study has shown is
is a good balance between efficiency and
accuracy~\citep{townsley.calder.ea:flame,townetal2009}.
This resolution and geometry was used in previous studies
allowing direct comparison to previous results~\citep{kruegetal12}.

@@

The transition from deflagration to detonation again follows
the previous studies, which assumed the transition location
is parameterized by the fuel density $\rho_{\mathrm{DDT}}$.
When a rising
plume reaches the threshold density, in this case
$\rho_{\mathrm{DDT}} = 10^{7.2}~\grampercc$,
a $12$~\km\ a region of fuel, (\C{12} and \Ne{20}, if present) is
fully burned $32$~\km\ radially outwards from the flame. This
instantaneous burning in the region of this size provides conditions
to generate the shock and support the detonation at the chosen
threshold density.  Multiple DDT points may arise, but they are
constrained to be at least $200$~\km\ apart. The choice of DDT
in the suite has been shown to be high enough to ensure
the robust ignition of a detonation shock.

@@

We frame the presentation of the results of the suites of simulations
principally in terms of the yield of \Ni{56}, the source of
the light curve of an event. \Ni{56} thus serves as a proxy
for the brightness of an explosion and comparison of the yields
is equivalent to comparing the brightness events. The
yields estimated from $Y_e$ and the NSE progress
variable, by assuming the composition in NSE is \Ni{56} plus equal
parts \Fe{54} and \Ni{58}, as described in
\citet{townetal2009,Meaketal09}.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
results are shown in blue. The curve for the hybrid models is shifted
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models.
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in \ref{fig:cumdist}.
The figure shows that the hybrid models consistently have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistently lower in explosions
from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}

@@

The estimated production of \Ni{56} as a function of simulation time
for 10 simulations of explosions from the hybrid progenitor is shown
in Figure \ref{fig:nithybrid} and from the traditional C-O progenitor is
shown in Figure \ref{fig:nitco}.
The figures show that the final estimated \Ni{56} for the C-O model is
slightly larger then the hybrid model. Therefore, the C-O produces more
\Ni{56}. The hybrid model has a larger range then the C-O model. Also, on
average, the CO model reaches the DDT phase sooner then the hybrid model.
Both figures show that production of \Ni{56} effectively ceases (the
curves flatten out) well before the end of the simulations at
$4.0$~\second. Also, the figures show that a few simulations
did not complete. {\color{red} OFFER A WHY?}

The degree of expansion was found using the time at which the first
detonation point occurred, and the mass at density less then 2e7 g/cc. The
estimated \Ni{56} Yield is the final estimated mass of the model.

@@

Figure \ref{fig:masshighdens} compares the final yield of IGEs
for the C-O and C-O-Ne simulation suites with the amount of expansion of the
WD during the deflagration phase. The amount of expansion is
characterized by the mass above $2 \times 10^7~\grampercc$ at the
time of the DDT, with more high-density mass
indicating less expansion during deflagration. The averages of both
the C-O and C-O-Ne suites along both axes are indicated by the shaded
regions with $\pm1\sigma$ widths.

As expected from previous studies, the trend for both C-O and C-O-Ne
models is that less expansion during the deflagration phase results in
greater IGE yields, because less expansion gives more high
density fuel to be consumed in the detonation.
being more high density fuel for the detonation to consume.
As the amount of expansion increases (the less
mass above $2 \times 10^7 \grampercc$),
for a similar amount of expansion, the C-O
models tend to yield greater IGE mass. Following
\citet{willcoxetal2016}, we interpret
the lower IGE yield in C-O-Ne models as resulting
from the lower \C{12} abundance and the fact that given
similar fuel density, the \Ne{20}-rich fuel will burn to cooler
temperatures than fuel in the C-O models. The result is
slower burning to IGE and thus a lower IGE yield.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:conversion}
Estimated yield of \Ni{56} as a function of final mass burned to IGE
for C-O-Ne progenitors (red) and C-O progenitors (blue) at
$t = 4.0 \second$.
}
\end{figure}
Figure \ref{fig:conversion} shows the estimated \Ni{56} yields
across the range of masses burned to IGE
for all C-O and C-O-Ne realizations at the end
of the simulations ($4.0 \second$),
at which point the total mass burned to \Ni{56} had become constant.
The difference between the two sets of results is more pronounced
than the difference between hybrid and tradition models
found by \citet{willcoxetal2016}. This difference follows from
differences in the electron capture rates, which follow from
{\color{red} two} reasons. {\color{red} HIGHER CENTRAL DENSITY?
MORE METALLICIY? HELP!}
%The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons.
%First is that higher critical density leads to higher electron capture resulting in less N\Ni{56}i56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
%NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
%hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18

@@

During the deflagration phase, the C-O models
on average burn more material to IGE and also had a significantly higher
fraction of IGE material that is \Ni{56}, yielding more \Ni{56} than
the C-O-Ne models. This result is counter to that observed in
\citet{willcoxetal2016}. During the detonation phase, the differences
are not as obvious and the final mass of IGEs are comparable. The
fraction of IGE material that is \Ni{56} at the end of the evolution,
however, is significantly higher. This result differs from
the results of \citet{willcoxetal2016} as well.

We attribute these differences as following from the different
compositions of the progenitors. The C-O-Ne hybrid progenitors
had more more neutron-rich material (a lower $Y_e$) than the
traditional C-O models. As expected, when this material burns
to IGEs, the proportion of neutron-rich material only gets
higher, as the results demonstrate.

The difference between these results and those of \citet{willcoxetal2016}
follows from the hybrid C-O-Ne progenitors having a different
temperature structure that led to ignition of the explosion at lower
densities. The C-O models in the \citet{willcoxetal2016} study
thus had more material burning at high densities and thus more
neutronization and a lower relative \Ni{56} yield than the
hybrid C-O-Ne models. In the case of the comparison here, the
C-O and hybrid C-O-Ne models {\color{red} the same central
temperature and density and very similar temperature and density
profiles at high densities, so the simulations in both cases
began with central ignitions. Differences in the explosion outcome
accordingly follow from differences in the composition.}

>>>>

The methodology of our study follows the approach of \citet{willcoxetal2016}.
We performed a suite of two-dimensional simulations of supernova explosions
from hybrid progenitors and compared the results to a suite of simulations
of explosions from traditional C/O progenitor models performed with the
same simulation code and from similar initial conditions. The simulations assumed
the deflagration to detonation transition explosion paradigm, and the
transition densities were the same in both suites. We briefly review our methodology
here, and refer the reader to previous work for additional details.
In particular, we use the same simulation instrument, a modified version
of the Flash Code, as \citet{willcoxetal2016} and we refer the reader there
for a description of modifications for C-O-Ne burning and verification tests
of the burning module.

@@

The simulations of supernova explosions presented here were performed
with a customized version of the \FLASH\ code, originally developed
at the University of Chicago.
Flash is a parallel, adaptive mesh, multi-physics simulation code
developed first for nuclear astrophysics applications and subsequently
for high-energy-density applications~\citep{Fryxetal00,calder.curtis.ea:high-performance,
calder.fryxell.ea:on,flash_pragmatic,flash_evolution}.
Flash has been applied to a variety of astrophysical problems by a host
of researchers, and the version we apply differs from other versions
principally in the modules describing thermonuclear burning via a
flame capturing model.

@@

For the deflagration phase, the flame capturing scheme propagates an
artificially broadened flame with an advection-diffusion-reaction (ADR)
scheme~\citep{Khok95,VladWeirRyzh06} via evolution of
a reaction progress variable to describe the consumption of C
and additional variables to describe the evolution of intermediate-mass
elements into the statistical quasi-equilibrium of the
Si-group~\citep{ifk1981,khok1981,khok1983} and then into iron-group elements
(IGEs) in full nuclear statistical equilibrium (NSE).

The reaction progress variable is $\phi$ and it varies from $\phi=0$ for
unburned fuel to $\phi=1$ for burned ash. $\phi$ is evolved
via an advection-diffusion-reaction equation,
\begin{equation}
  \label{eq:ard}
  \partial_t \pv + \vec{u}\cdot\nabla \pv = \kappa \nabla^2 \pv +
\frac{1}{\tau} R\left(\phi\right) ,
\end{equation}
where $\vec{u}$ is the velocity of the fluid, $\kappa$ is the
diffusion coefficient, $\tau$ is the reaction timescale, and $R(\phi)$ is
a non-dimensional function describing the reaction. The parameters
$\kappa$, $\tau$, and $R(\phi)$ are tuned to propagate the reaction
front at a prescribed speed.  Our model uses the ``sharpened KPP''
 described by~\cite{VladWeirRyzh06},
with $R\propto(\phi-\epsilon)(1-\phi+\epsilon)$, where
$\epsilon \simeq 10^{-3}$.  This scheme has been shown to be
acoustically quiet, stable, and to give a unique flame speed
\citep{townsley.calder.ea:flame}. The input flame speeds come from
tabulated results obtained by direct numerical simulations of
thermonuclear burning~\citep{timmes92,Chamulak2007The-Laminar-Fla},
and
these are boosted to account for speed-up of burning due to unresolved
buoyancy and background turbulence~\citep{Khok95,
gamezo.khokhlov.ea:thermonuclear,townsley.calder.ea:flame,jacketal2014}.

The two-dimensional models in this study do not utilize a sub-grid-scale
model for the turbulence-flame
interaction~\citep[See][for examples]{Schmetal06a,Schmetal06b,jacketal2014}.
Those sub-grid-scale models only apply in three-dimensional
simulations because two-dimensional hydrodynamics cannot
correctly describe turbulence. The simulations we present
use the minimal enhancement based on the Rayleigh-Taylor
strength introduced by~\citet{townsley.calder.ea:flame}. The
assumption here is that the burning self-regulates on resolved
scales so that results are insensitive to the detailed treatment
of the interaction with turbulence, and previous experience
indicates this assumption is reasonable for comparisons
like the one presented in this work~\citep{townsley.calder.ea:flame,
willcoxetal2016}.

The ADR scheme describes the consumption of C and the subsequent stages
are described by separate progress variables and
separate relaxation times derived from full nuclear network calculations
\cite{Caldetal07,townetal2016}. In both the quasi-equilibrium and full equilibrium,
the creation of light elements by photodisintegration balances the creation of heavy
elements by fusion, maintaining the equilibrium. The relative balance depends on
thermodynamic conditions, e.g.\ density and temperature, and hydrodynamic motion
during the explosion changes the thermodynamic conditions and thus the
balance.
{\color{blue} Electron capture also influences the evolution in several ways by
neutronizing the material, which produces more neutron rich iron-group
material at the expense of \Ni. Neutronization also shifts the binding
energy of the material and the Fermi energy of electrons, respectively
changing the temperature (due to released energy) and the pressure.
Finally, individual electron capture reactions emit neutrinos that
escape and remove energy from the system.}
Like the input flame speed, the burning model includes tabulated rates for these effects
from detailed NSE calculations ~\citep{SeitTownetal09}. Accordingly, the burning
model is able to describe dynamic evolution of the ash in addition to the
stages of C-O-Ne burning.

The burning model also describes the detonation phase with progress variables.
In this case, the model evolves thermally-activated burning with the actual
temperature-dependent rate for C consumption, which allows a propagating shock to
trigger burning, i.e.\ to propagate a detonation front. The propagating detonation
is able to describe the same stages of C burning as the deflagration case, including
the relaxation into NSE~\cite[and references therein]{townetal2016}. Finally,
we again note that the burning model was adapted for the case of burning in
hybrid white dwarfs. Direct numerical simulations of burning that guided
the modifications, details of the modifications to the burning model, and
verification tests may be found in \citet{willcoxetal2016}.

@@

The hybrid white dwarf model that served as the initial condition
for the simulations of supernova explosions presented in this work
was constructed with the one-dimensional stellar evolution code
MESA~\citep{mesa1,mesa2,mesa3,mesa3e}. The evolution of the model
included thermohalene mixing during the cooling phase and thus
had a lower C fraction than previous hybrid models~\citep{brooksetal2017}.
The hybrid model was constructed to have conditions as similar a possible
to a ``classic'' C/O model and the two shared the same central temperature
and density.  Figure~\ref{fig:init_conds} shows the density and temperature
profiles of the two initial one-dimensional models.
\begin{figure}
\includegraphics[width=\columnwidth]{figures/initial_conds.png}
\caption{\label{fig:init_conds}
Temperature, density, and  composition profiles of the one-dimensional hybrid
progenitor WD. The central temperature and density were the same as
the traditional C/O progenitor model.
The peak temperature of the hybrid model is at the center of the star,
so both the hybrid and traditional models could share the same
	central ignition initial conditions.
}
\end{figure} 
{\color{blue} We centrally ignite our explosion simulations for both
  C/O and hybrid models to coincide with the peak temperature at the
  center of the WDs, unlike the hybrid models
  of~\citet{willcoxetal2016}.}

@@

The initial progenitor models for the two-dimensional simulations were
created from the one-dimensional \MESA\ models by mapping the one-dimensional
models onto the two-dimensional domain while
preserving hydrostatic equilibrium.
As described above, the flame capturing scheme with progress
variables describes the evolution as the material burns. The \MESA\
models, however, relied on a detailed reaction network that included
many species. Accordingly, the process of creating the two-dimensional
models for \FLASH\ required aggregating some of the species abundances.
As with much of this study, we applied the
techniques of~\citet{willcoxetal2016}.

The process of mapping the \MESA\ models began by converting
the \MESA\ model to a uniform grid of $4$~km resolution. 
{\color{blue}We mass-weighted and averaged quantities in \MESA\ zones with spacing less than $4$~km
and quadratically interpolated quantities in \MESA\ zones with spacing greater than $4$~km.}
At this point,
abundances of nuclides from the \MESA\ models were aggregated
into the abundances tracked by the flame capturing scheme in
\FLASH.
The most abundant isotopes in the model were \C{12}, \Ox{16},
and \Ne{20}, which are symmetric (the number of neutrons
equals the number of protons). Similarly to~\citet{willcoxetal2016},
other neutron-rich isotopes in the initial model were combined into
\Ne{22}, which serves as a proxy for metallicity. The aggregation
accounts for the $Y_e$ of the full set of nuclides, and \Ne{20}
and \Ox{16} were constrained to be in the same ratio in both
sets of abundances. \figref{fig:init_conds} shows the initial
profile of the one-dimensional models.

The original \MESA\ model was in equilibrium, but to ensure
the uniformly-gridded model was in hydrostatic equilibrium we
constructed the appropriate pressure profile. This was done by
integrating for the pressure in each zone from the central point up,
accounting for the local acceleration of gravity, temperature,
composition, and the mass below and enclosed by the zone. As
with \citet{willcoxetal2016} we used the EOS routine from
\CASTRO\ ~\citep{timmes.swesty:accuracy,castro1}.\footnote{The
Helmholtz EOS table used in \CASTRO\ is in the public BoxLib
Microphysics repository at
  \url{https://github.com/BoxLib-Codes/Microphysics.git} (commit
  hash $\mathrm{45ed859b6c1dc80d831d93f9728986d6ad6e1ddc}$).} As
 with the models in \citet{willcoxetal2016}, this procedure produced
 a structure that was stable in \FLASH, with fluctuations in central
density less than $3\%$, for at least $5$ seconds with no energy
deposition.

\subsection{DDT Process and Suites of Explosions}

The simulations performed for this study consisted of a suite of
{\color{red} 35 CHECK THIS! 40?} two-dimensional simulations of
thermonuclear supernova
explosions from hybrid C-O-Ne progenitors in the DDT explosion paradigm. These
were compared to a suite of supernova simulations from traditional
C-O progenitors. In both suites, the simulation
begins with a progenitor model mapped to the two-dimensional
\FLASH\ grid. The burning is initiated with a ``match head,'' a region
in the white dwarf's center that is fully burned to nuclear statistical
equilibrium (NSE).
This initially burned region ignites a deflagration, a subsonic
flame, and because the match head was perturbed it is unstable to
the Rayleigh-Taylor instability with the result that buoyant plumes
rise. The star is partially consumed during this deflagration phase,
and the star responds by expanding.
When a plume reaches a specified density,
a detonation is initiated, and the simulation continues until
the expanding star reaches low densities at which point burning
effectively ends. The paragraphs in this section provide details
of the implementation of this method.

@@

The simulations were performed in two-dimensional $\mathrm{z-r}$
cylindrical coordinates, extending radially from 0 to
$65,536$~\km\ and along the axis of symmetry from $-65,536$~\km\ to
$65,536$~\km. The maximum refinement level of the adaptive mesh
corresponded to $4$~\km\ resolution, which previous study has shown
is a good balance between efficiency and
accuracy~\citep{townsley.calder.ea:flame,townetal2009}.
This resolution and geometry was used in previous studies
allowing direct comparison to previous results~\citep{kruegetal12}.

@@

The transition from deflagration to detonation again follows
the previous studies, which assumed the transition location
is parameterized by the fuel density $\rho_{\mathrm{DDT}}$.
When a rising
plume reaches the threshold density, in this case
$\rho_{\mathrm{DDT}} = 10^{7.2}~\grampercc$,
a $12$~\km\ region {\color{blue} [radius or diameter?]} of fuel, (\C{12} and \Ne{20}, if present) is
fully burned $32$~\km\ radially outwards from the flame. This
instantaneous burning in the region of this size provides conditions
to generate the shock and support the detonation at the chosen
threshold density.  Multiple DDT points may arise, but they are
constrained to be at least $200$~\km\ apart. The choice of DDT
in the suite has been shown to be high enough to ensure
the robust ignition of a detonation shock.

@@

We frame the presentation of the results of the suites of simulations
principally in terms of the yield of \Ni{56}, the energy source of
the light curve of an event. \Ni{56} thus serves as a proxy
for the brightness of an explosion and comparison of the yields
is equivalent to comparing the brightness of events. The
yields were estimated from $Y_e$ and the NSE progress
variable, by assuming the composition in NSE is \Ni{56} plus equal
parts \Fe{54} and \Ni{58}, as described in
\citet{townetal2009,Meaketal09}.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/ni56_yield_cum_dist.pdf}
\caption{\label{fig:cumdist}
The cumulative distribution of the final \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models. The hybrid results are shown in red, and the CO
results are shown in blue. The curve for the hybrid models is shifted
to the left, indicating that explosions from hybrid progenitors produce
less \Ni{56} than explosions from traditional C-O models.
}
\end{figure}
The cumulative distribution of the \Ni{56} yield for explosions from
C-O and hybrid C-O-Ne models is presented in Figure \ref{fig:cumdist}.
The figure shows that the hybrid models consistently have a higher
cumulative fraction at a given mass of \Ni{56}, which indicates
that the yields of \Ni{56} are consistently lower in explosions
from hybrid progenitors. {\color{red} CHECK/EXPAND THIS}

@@

The estimated production of \Ni{56} as a function of simulation time
for 10 simulations of explosions from the hybrid progenitor is shown
in Figure \ref{fig:nithybrid} and from the traditional C-O progenitor is
shown in Figure \ref{fig:nitco}.
{\color{blue} The figures show that the final estimated \Ni{56} for
  the C-O model is slightly larger than the hybrid model. Therefore,
  the C-O produces more \Ni{56}. The hybrid model has a larger range
  then the C-O model. [Figure \ref{fig:nithybrid} and Figure
  \ref{fig:nitco} cannot support general claims like this because they
  only show ten of our realizations and it's hard to measure by
  eye. Figure \ref{fig:cumdist} is much better at demonstrating both
  of these statements.]}
Also, on average, the CO model reaches the DDT phase sooner then the
hybrid model.  Both figures show that production of \Ni{56}
effectively ceases (the curves flatten out) well before the end of the
simulations at $4.0$~\second. Also, the figures show that a few
simulations did not complete. {\color{red} OFFER A WHY?}

\blust{The degree of expansion was found using the time at which the first
detonation point occurred, and the mass at density greater than 2e7 g/cc. The
estimated \Ni{56} Yield is the final estimated mass of the model.}

@@

Figure \ref{fig:masshighdens} compares the final yield of IGEs
for the C-O and C-O-Ne simulation suites with the amount of expansion of the
WD during the deflagration phase. The amount of expansion is
characterized by the mass above $2 \times 10^7~\grampercc$ at the
time of the first DDT occurrence, with more high-density mass
indicating less expansion during deflagration. The averages of both
the C-O and C-O-Ne suites along both axes are indicated by the shaded
regions with $\pm1\sigma$ widths.

As expected from previous studies, the trend for both C-O and C-O-Ne
models is that less expansion during the deflagration phase results in
greater IGE yields because less expansion allows the detonation to
consume more high density fuel.
As the amount of expansion increases (less
mass remains above $2 \times 10^7~\grampercc$),
for a similar amount of expansion, the C-O
models tend to yield greater IGE mass. Following
\citet{willcoxetal2016}, we interpret
the lower IGE yield in C-O-Ne models as resulting
from the lower \C{12} abundance and the fact that given
similar fuel density, the \Ne{20}-rich fuel will burn to cooler
temperatures than fuel in the C-O models. The result is
slower burning to IGE and thus a lower IGE yield.

\begin{figure}
\includegraphics[width=\columnwidth]{figures/FMBTI_v_Ni56Yield_plot.pdf}
\caption{\label{fig:conversion}
Estimated yield of \Ni{56} as a function of final mass burned to IGE
for C-O-Ne progenitors (red) and C-O progenitors (blue) at
$t = 4.0 \second$.
}
\end{figure}
Figure \ref{fig:conversion} shows the estimated \Ni{56} yields
across the range of masses burned to IGE
for all C-O and C-O-Ne realizations at the end
of the simulations ($4.0 \second$),
at which point the total mass burned to \Ni{56} had become constant.
The difference between the two sets of results is more pronounced
than the difference between hybrid and traditional C/O models
found by \citet{willcoxetal2016}. This difference follows from
differences in the electron capture rates, which follow from
{\color{red} two} reasons. {\color{red} HIGHER CENTRAL DENSITY?
MORE METALLICIY? HELP!}
%The conversion of \Ni{56} to IGEs are more pronounced in my case. There are two assumptions as to why figure 6 is more pronounced in my paper then in Dons.
%First is that higher critical density leads to higher electron capture resulting in less N\Ni{56}i56 produced. Figure 4 shows that CO model has a stronger electron capture then the hybrid model. The second is that the central ignition leads to early burning at higher density. Both of these cases lead to more electron capture resulting in a larger difference in evolution between the models.
%NEW: Production of 56Ni and mass burned to IGEs for CO (red) and
%hybrid CONe (green) WD realizations. SAME AS DON'S FIG 18

@@

During the deflagration phase, the C-O models
on average burn more material to IGE and also had a significantly higher
fraction of IGE material that is \Ni{56}, yielding more \Ni{56} than
the C-O-Ne models. This result is counter to that observed in
\citet{willcoxetal2016}. During the detonation phase, the differences
are not as obvious and the final mass of IGEs are comparable. The
fraction of IGE material that is \Ni{56} at the end of the evolution,
however, is significantly higher for C/O models than for our hybrid models. 
{\color{blue}This result differs from the results of
  \citet{willcoxetal2016} as well and is consistent with the
  observation that our hybrid models on average expand less during the
  deflagration stage than our C/O models. By contrast, the hybrid models of
  \citet{willcoxetal2016} expanded very slightly more
  than C/O models on average during the deflagration stage.}

We attribute these differences as following from the different
compositions of the progenitors. The C-O-Ne hybrid progenitors
had more neutron-rich material (a lower $Y_e$) than the
traditional C-O models. As expected, when this material burns
to IGEs, the proportion of neutron-rich material only gets
higher, as the results demonstrate.

The difference between these results and those of
\citet{willcoxetal2016} follows from their hybrid C-O-Ne progenitors
having a different temperature structure that
led to ignition of the explosion at lower densities.
The C-O models in the \citet{willcoxetal2016} study
thus had more material burning at high densities and thus more
neutronization and a lower relative \Ni{56} yield than the
corresponding hybrid C-O-Ne models. In the case of the comparison here, the
C-O and hybrid C-O-Ne models {\color{red} have the same central
temperature and density and very similar temperature and density
profiles at high densities, so the simulations in both cases
began with central ignitions. Differences in the explosion outcomes
for our C/O and hybrid C-O-Ne WD models 
accordingly follow from differences in their composition.}
